\section{Server Side}
At the server side the Morfeas WEB have some PHP scripts that handle requests from the client. This scripts runs via the PHP engine that executed as module of the Apache WEB server.
The PHP scripts located under the ``Morfeas\_php" directory. Also the outputs (Loggers, Logstats) of the Morfeas components exported at local directory ``/mnt/ramdisk/" where is 
linked as source directory to Apache and can be access from alias ``./ramdisk". At this aliased directory the exported Logstat for all the Morfeas components can be found and at
subdirectory ``Morfeas\_Loggers" the Loggers of the components.\\
The Logstats are exported every second in JSON format and contains the current state of the device(s) that are handled by a Morfeas component. The Logger of a component is 
a text file in human readable format and contains the chronological reports of the component.     

At the following subsections are attributed to the PHP scripts of the Morfeas WEB.

\subsection{Morfeas\_Web\_if.php}
The PHP script file Morfeas\_Web\_if.php contains the functionality to provide the Logstat files at the client request and to receive ISO Channels configuration objects.
The script can be called as ``./morfeas\_php/Morfeas\_Web\_if.php" and accept ``GET" and ``POST" requests.
\subsubsection{GET request}
In every call with ``GET"" request the Morfeas\_Web\_if.php script expecting an argument ``COMMAND" with value the one of the allowed commands.
At the table~\ref{table:Morfeas_Web_if} will present the allowed commands for the Morfeas\_Web\_if.php script.

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|}
 \hline
 \textbf{Command} & \textbf{Description} & \textbf{Content type}\\
 \hline
 logstats & Return all logstat combined & JSON \\
 logstats\_names & Return the filenames of the available logstat & JSON \\
 loggers & Return the filenames of the Morfeas component logger & JSON \\
 opcua\_config & Return the current ISO Channel configuration & JSON\\
 \hline
\end{tabular}
\caption{GET request values for argument ``COMMAND"}
\label{table:Morfeas_Web_if}
\end{table}

If the GET request made without the argument ``COMMAND" or with an unknown value in to it, the return will be ``HTTP ERROR 404".

\subsubsection{POST request}
The ``Morfeas\_Web\_if.php" script is also accept ``POST" requests in order of new configurations for the ISO Channel object of the OPC-UA.
The contents for this kind of request is a JSON object with tag name ``data" where contains an array with the configuration for each ISO Channel.
Every element of the array contain a JSON object with the configuration for each particular ISO channel. The structure for the argument for this POST request
presented at listing~\ref{lst:Morfeas_Web_if}.

\begin{lstlisting}[frame=single,caption=Example for argument of POST request for Morfeas\_Web\_if.php,label=lst:Morfeas_Web_if]
{"data":[
   {
      "ISOChannel":"Name of the ISO Channel",
      "IF_type":"MDAQ"|"SDAQ"|"IOBOX"|"MTI",
      "Anchor":"The anchored physical input with the current ISO Channel",
      "Description":"Description of the ISO Channel",
      "Max":"Minimum input value",
      "Min":"maximum input value",
      "Unit":"Unit of measurements (Not needed for SDAQ IF_type)"
   },...
 ]
}
\end{lstlisting}

In every success the ``Morfeas\_Web\_if.php" return a JSON object with a report, otherwise return a string with the error that cause it to fail.

\subsection{config.php}
The ``config.php" is a PHP script part of the Morfeas WEB where is responsible for each configuration of the computer and the Morfeas System. It's can called from ``./morfeas\_php/config.php",
and accept ``GET" and ``POST" HTTP requests. At the following subsection the functionality and data the can be exchange via this script will be explained in details.

\subsubsection{GET request}
For accept a ``GET" request the ``config.php" is required to received the request with the argument ``COMMAND" that have a specific value that explain the request that the client want.
At the table~\ref{table:GET_config} derived a list with the allowed values and descriptions for the functionality of each one.

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|}
 \hline
 \textbf{Command} & \textbf{Description} & \textbf{Content type}\\
 \hline
 getbundle & Return a .mbl file with wholly Morfeas System configuration & File \\
 getISOstandard\_file & Make a force download of current ISOStandard file & File \\
 getCurConfig & Return the current Internet and NTP configuration& JSON \\
 timedatectl & Return the output of timedatectl & HTML \\
 getMorfeasConfig & Return the current Morfeas system configuration & XML \\
 getISOstandard & Return an instance of the current ISOStandard file & XML \\
 getCANifs\_names & Return the available CANBus interfaces & JSON \\
 \hline
\end{tabular}
\caption{GET request values for argument ``COMMAND"}
\label{table:GET_config}
\end{table}

In case that the value of argument ``COMMAND" is not valid or if the argument is missing the script will return ``HTTP ERROR 404".

\subsubsection{POST request}

The ``config.php" script accept also POST HTTP requests that caries out configurations for the computer and the Morfeas System.
The script steering the functionality according to the ``CONTENT\_TYPE" of the HTTP message that the client sent to the server.
The data that contained in the POST request message must be compressed with the internally implemented ``compress" function.
At table~\ref{table:POST_config} will be present all the allowed set values for the ``CONTENT\_TYPE" of a POST request.

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|}
 \hline
 \textbf{Content type} & \textbf{Description} & \textbf{Contents Data}\\
 \hline
 net\_conf & Request with new config for Hostname, INET, CAN, NTP & JSON \\
 Morfeas\_config & Request with new configuration for Morfeas system & XML\\
 ISOstandard &  Request with new ISOStandard &  XML\\
 Morfeas\_bundle*** & Request with a restoring bundle file & MBL \\
 reboot & Request for computer reboot & VOID \\
 shutdown & Request for computer power off & VOID \\
 \hline
\end{tabular}
\caption{Content types for POST request}
\label{table:POST_config}
\end{table}
\par*** Post request with ``Morfeas\_bundle" as Content type does not required any compression on data.
\newpage
The contain structure of a ``net\_config" type request present at listing~\ref{lst:net_config}.
\begin{lstlisting}[frame=single,caption=Structure of contents for POST request with ``contents\_type:net\_config",label=lst:net_config]
{
  "hostname":"Computer's Hostname",
  "mode":"DHCP"|"Static",//Internet configuration
  "ip":###,"mask":#,"gate":###, <- Used if mode == "Static"
  "ntp":###,//IPv4 of NTP server
  "CAN_ifs"://Only if CANBus adapters are available
    [
     {
       "if_Name":"Name of CANBus interface",
       "bitrate":#//In bits per second
     },
     ....
    ]
}
\end{lstlisting}

***The variables that present settings that will not be configured can be excluded from the object.\\
\#Every variable that representing IPv4 stored as signed integer number that presenting the 32 bit's of the IPv4 address in big-endian form.\\
eg. The IPv4 \textbf{``100.45.78.10"} will represent by $\mathbf{(1680690698)_d}$.\\

The data contents of a POST request with with contents\_type:``Morfeas\_config" is send in XML format that follow the standard of the Morfeas System.
More information for this at reference guide of the Morfeas Core project.

The data contents of a POST request with with contents\_type:``ISOstandard" is also send in XML format, an example of the structure for this derived at listing~\ref{lst:ISOStandard}.\\
Every child node of node ``points" is present an ISOStandard, then name tag of each is the name that will used as ISOChannel. The children of every ISOStandard must be four in total
with tags \textbf{description, unit, max, min} in this order. The content of every child represent each name tag.

\begin{lstlisting}[frame=single,caption=Structure of contents for POST request with ``contents\_type:ISOstandard",label=lst:ISOStandard]
<?xml version="1.0" encoding="UTF-8"?>
<root>
  <points>
    <ISOStandard_name_tag>
      <description>Description of ISOStandard</description>
      <unit>Default Unit</unit>
      <max>Maximum value</max>
      <min>Minumum value</min>
    </ISOStandard_name_tag>
    ....
  </points>
</root>
\end{lstlisting}

Post request with contents\_type:Morfeas\_bundle used to upload and reconfigure the Morfeas System and the ISOChannel of the Morfeas OPC-UA server on a previous state.
The contents of this request type is a binary .mbl file. Also this request does not required any compression of the contents.\\

The last two request ``reboot" and ``shutdown" used in order to reboot and shutdown the computer respectively.\\

The return of the script in success will be a JSON report for ``net\_conf" and ``Morfeas\_config" contents\_type and a human readable string for ``ISOstandard", ``Morfeas\_bundle".
In case of failure the script will answer with a human readable string with the error that cause it to fail, or with an ``HTML ERROR 404" in case that the contents\_type is unknown.

\subsection{Morfeas\_dbus\_proxy.php}
The Morfeas\_dbus\_proxy.php is a PHP script part of the Morfeas WEB project that made to act as a proxy between the WEB and the Morfeas components that have D-BUS functionality.
THis script can be called from ``./morfeas\_php/Morfeas\_dbus\_proxy.php" and accepting only POST requests. The POST request which is send to this script must contain an argument ``arg"
with value a JSON object (example~\ref{lst:dbus_proxy}) that will give to the script the information of to which Morfeas component the data will go,
the type of the device that will be handled, the D-BUS method that will be called and the contents of the D-BUS message.

\begin{lstlisting}[frame=single,caption=Structure of contents for POST request for Morfeas\_dbus\_proxy.php,label=lst:dbus_proxy]
{
  "handler_type":"Morfeas Handler component's name",
  "dev_name":"Device name",
  "method":"D-BUS method",
  "contents":{"Object with the data that will send to handler"}
}
\end{lstlisting}

\subsection{Morfeas\_SDAQnet\_proxy.php}
